Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-25 Referee1_Response.tex

\noi xxx 
We thank the referee for this suggestion. 
You are right.
There are cases when generating scenarios is expensive in the stochastic optimization setting as well. 
We changed the introduction based on your, the associate editor and the other reviewer's comments. 
We specifically added this as a motivation. 
\medskip

\begin{itemize}
\item[] \textit{However, perhaps more often, sampling the i.i.d. realizations is computationally cheap compared to solving the resulting SAA instances in stochastic optimization. 
In this latter case, we have a choice between simply increasing the number of batches in a non-overlapping method or using the overlapping batch means approach (with some degree of overlap) in order to reduce variance.
Based on the paper's results, perhaps the computational effort required to achieve a level of variance reduction should guide this choice. 
The authors do point to the fact that warm starts in a stochastic
optimization algorithm can be exploited much more easily when using overlapping batch means than when not using overlapping batches. 
Some attempt to explore this tradeoff would be valuable. 
The computational results use sorting (for the news vendor problem), a dynamic programming algorithm (for a stochastic knapsack model), and a decomposition method (for two-stage stochastic linear programs). 
While I am not suggesting that this exploration needs to be made for all three types of algorithms, even exploring it in the case of the sorting algorithm (where some algorithms are well suited for almost-sorted lists) could provide valuable insight.}
\end{itemize}

\noi 
Based on your and the associate editor's comments, we studied the computational efficiency of the OMRP estimators. 
The results of this study are presented in a new section, Section 5.4 (Computational Efficiency).
%We studied the computational efficiency of the OMRP estimators, based on your and the associate editor's comments, and provided a summary of our results in a new section, Section 5.4 (Computational Efficiency). 
We first approached efficiency by the reciprocal of variance multiplied by the computation time, per associate editor's suggestion. 
Maximizing the computational efficiency defined in this manner provided guidelines on selecting the degree of overlap. 
We then looked at how OMRP compared to increasing the number batches in MRP.
We examined computational efficiency both theoretically and empirically. 
For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions. 
We found that when effective warm-starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.  
All these results are presented in Section 5.4 (Computational Efficiency). 
Thank you for this suggestion. 
We believe the study of computational efficiency significantly improved the paper. 
\medskip

@@

\begin{itemize}
\item[16.] \textit{p17, l55: Perhaps add a comment on why DB1 may not experience the asymptotic variance reduction? 
(Is it because it may lack a unique solution?)}
\end{itemize}

\noindent
Done.
% xxx Yes, it is partially because we are not sure if it has a unique optimal solution as DB1 has never been solved before. 
%Even if it has been solved, the variance reduction is shown asymptotically but the computations are only for small sample sizes. 
%We reworded this to reflect these points.
%Thank you for this suggestion. 
\medskip

\begin{itemize}
\item[17.] \textit{p18, figures: The figures are a bit small and hence can be hard to read without enlarging them (but perhaps this will be taken care of at production).}
\end{itemize}

\noindent 
We split these two figures into three and enlarged each graph. 
We also enlarged the legends in these graphs to improve clarity.
All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger, with legible legends. 
\medskip

@@

\begin{itemize}
\item[18.] \textit{p18, l57: The authors speak of coverage probabilities for DB1, but how can this be done without knowing an optimal solution to DB1?}
\end{itemize}

\noindent 
We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP CIs for this test problem.
We explain this at the end of Section 5.1 (Test Problems). 
We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for DB1. 
\medskip

\begin{itemize}
\item[19.] \textit{p19: It may be possible to expand on the last paragraph of Section 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
\end{itemize}

\noindent 
Thank you for this suggestion. 
Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
Please note that this guidance appears in the third and last paragraphs of the new section, Section 5.4 (Computational Efficiency).

### 2014-06-25 AE_Reponse.tex
Changes to R1 and AE responses

\noi xxx 
We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your and the referees' comments and the new material like computational efficiency added to the paper.
\medskip

@@

\noi 
Thank you for this suggestion. 
It is indeed important to study computational efficiency in this context. 
We created a new section, Section 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
We discussed efficiency for a given functional form of the solution time per batch. 
Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
We illustrated this method on the newsvendor problem using insertion sort. 
Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping. 
We discussed guidelines on selecting the degree of overlapping (for NVD or for a given generic problem) in Section 5.4 (Computational Efficiency). 
\medskip

In addition, based on the comments of Referee 1, we also studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances. 
Our results indicate that when warm-starting is effective, overlapping is computationally more efficient than increasing the number of batches of MRP.
We also illustrated this result on the newsvendor problem. 
We believe the paper has improved as a result of the study of computational efficiency. 
Thank you. 
\medskip

>>>>

\noi xxx 
We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your and the referees' comments. 
The revised introduction also includes several new comments based on the material added to the paper (computational efficiency) and a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion). 
\medskip

@@

\noi 
Thank you for this suggestion. 
It is indeed important to study computational efficiency in this context. 
We created a new section, Section 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
We discussed efficiency for a given functional form of the solution time per batch. 
Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
We illustrated this method on the newsvendor problem using insertion sort. 
Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping. 
We discussed guidelines on selecting the degree of overlapping. 
\medskip

In addition, based on the comments of Referee 1, we studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances. 
Our results indicate that when warm-starting is effective, overlapping is computationally more efficient than increasing the number of batches of MRP.
Even in cases where warm-starting is less effective, computational efficiency can be observed when about 10\% of observations are overlapped.
We again illustrated this result on the newsvendor problem. 
We believe the paper has improved as a result of the study of computational efficiency. 
Thank you. 
\medskip
